---
title: "R Notebook"
output: html_notebook
---
# Question 3
Open the file EconomicsJournalSubscriptionData.csv, it contains data about subscriptions to economic journals at US libraries for the year 2000. Your job is to create a model with the number of subscribers (subs) as the dependent variable. Use the following variables:
    • Price of the journal (price)
    • Number of citations (citations)
    • Characters per page (charpp
    • Year of first publication (foundingyear)
There might be non-linear relationships in the model, investigate if this is the case and if so, show this in a graph. Present a model without any transformation and one with the appropriate transformations. Which models fits better?


```{r}
library(class)
library(magrittr)
library(dplyr)
library(caret)
library(ggplot2)
library(fastDummies)
library(stargazer)
library(reshape2)
#library(texreg)
#library(AER)
library(stringr)
```

# Data understanding

```{r}
economy_data <- read.csv("/home/ds/Desktop/556000 Exam_FIML/556000EconomicsJournalSubscriptionData.csv")

names(economy_data)
unique(economy_data$Abbreviation)
# Choosing the vars that will be used

ecodata <- economy_data[,c(5,7,8,9,10)]
summary(ecodata)

```

# Data Understanding and Prep


```{r}
unique(ecodata$foundingyear)
summary(ecodata)
nrow(ecodata)

ecodata$age <- 2000 - ecodata$foundingyear
head(ecodata)

```
- 150 rows
- NO missing values. 
- All are continuous var. 
- Proportions are not close to each other (charpp vs sub). Year?


```{r}
ggplot(ecodata,aes(x=price, y=subs)) +geom_point() +geom_smooth(method=loess)
ggplot(ecodata,aes(x=citations, y=subs)) +geom_point() +geom_smooth(method=loess)
ggplot(ecodata,aes(x=charpp, y=subs)) +geom_point() +geom_smooth(method=loess)
ggplot(ecodata,aes(x=age, y=subs)) +geom_point() +geom_smooth(method=loess)
```
There are multiple nonlinear relationships
    - Subs and foundingyear have polynomial relationship
    - Subs and price looks like poly as well.
    - Citations and Subs have a poly rel. 

Outliers might be influencing the relationships:


# Reg

```{r}

modelx<- lm(subs~citations, data = ecodata)
modely<- lm(subs~price, data = ecodata)
modelz<- lm(subs~age, data = ecodata)
modelq<- lm(subs~charpp, data = ecodata)
modelzz <- lm(subs~price+citations+charpp+age, data = ecodata)



# Price - Subs
model1 <- lm(subs~price, data = ecodata)
model2 <- lm(subs~log(price), data = ecodata) # Fits
model3 <- lm(subs~poly(price,2), data = ecodata)
# Citations - Subs
model4 <- lm(subs~citations, data = ecodata)
model5 <- lm(subs~log(citations), data = ecodata)
model6 <- lm(subs~poly(citations,2), data = ecodata) # Fits
model7 <- lm(log(subs)~citations, data = ecodata)
# CHarpp - Subs
model8 <- lm(subs~charpp, data = ecodata)
model9 <- lm(subs~log(charpp), data = ecodata) ### NO Fit
model10 <- lm(subs~poly(charpp,2), data = ecodata) 
model11 <- lm(log(subs)~charpp, data = ecodata)
# foundingyear - Subs
model12 <- lm(subs~foundingyear, data = ecodata)
model13 <- lm(subs~log(foundingyear), data = ecodata) 
model14 <- lm(subs~poly(foundingyear,2), data = ecodata) # Fits 
model15 <- lm(log(subs)~foundingyear, data = ecodata)



modelx <- lm(subs~scale(log(price))+scale(poly(citations,2))+scale(charpp)+scale(poly(age,2)), data = ecodata)
#summary(model1)

stargazer(modelzz, modelx, header = FALSE, align = TRUE, title ="Table 1.EconomyJournalSubs", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")
```









