---
title: "R Notebook"
output:
  html_notebook: default
  pdf_document: default
  word_document: default
---
# Question 6
The file graduate_earnings.csv contains data about the earnings of alumni from different schools in the United States. Alumni were asked what their yearly earnings (Earn) were 5 years after graduating. Present a model predicting how much money alumni make after 5 year (Earn) using the following independent variables:
    • Whether their university is public or private (Public)
    • Their SAT (SAT)
    • The tuition fee (Price)
    • How much of their tuition fee was paid for through a scholarship (need_fraction)
Some of the variables have missing observations, identify which these are and deal with them accordingly. Then present a model where you dealt with the missing values and compare this to the model that excluded the missing data. Is there a difference between the models? Which model would you prefer?

```{r}
library(class)
library(magrittr)
library(dplyr)
library(caret)
library(ggplot2)
library(fastDummies)
library(stargazer)
library(reshape2)
#library(texreg)
#library(AER)
library(stringr)
```

# Data understanding

```{r}
# !Original csv file did not work with utf-8. Deleted the unknown char from csv columns names manually. 

g_eraning_data <- read.csv("/home/ds/Desktop/556000 Exam_FIML/556000graduate_earnings.csv", sep = ",")

summary(g_eraning_data)
# Choosing the vars that will be used

gdata <- g_eraning_data[,c(4,2,5,6,7)]
summary(gdata)

```

# Data Understanding and Prep

```{r}
unique(gdata$Public)
summary(gdata)
nrow(gdata)
```
Public is categorical, 1,0
NA=Public, SAT, need_fraction
Std is needed
600 rows



```{r}
ggplot(gdata,aes(x=Public, y=Earn)) +geom_point() +geom_smooth(method=loess) # Public seems to have no relationship
ggplot(gdata,aes(x=SAT, y=Earn)) +geom_point() +geom_smooth(method=loess) # Increasing increase
ggplot(gdata,aes(x=Price, y=Earn)) +geom_point() +geom_smooth(method=loess) # poly might fit better
ggplot(gdata,aes(x=need_fraction, y=Earn)) +geom_point() +geom_smooth(method=loess) # might be linear
```


# Initial Reg

```{r}

gmodel<-lm(Earn~Public, data = gdata)
gmodel1<-lm(Earn~SAT, data = gdata)
gmodel2<-lm(Earn~Price, data = gdata)
gmodel3<-lm(Earn~need_fraction, data = gdata)

#Controling

gmodelc <- lm(Earn~Public+SAT+Price+need_fraction, data = gdata)
stargazer(gmodelc, header = FALSE, align = TRUE, title ="Table 1. Graduate Earning", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")

stargazer(gmodel,gmodel1,gmodel2,gmodel3, header = FALSE, align = TRUE, title ="Table 1. Graduate Earning", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")
```
#Tranformation

```{r}
#SAT
gm<- lm(Earn~log(SAT), data = gtransdf)
gm1<- lm(Earn~scale(poly(SAT,2)), data = gtransdf)
gm2<- lm(log(Earn)~SAT, data = gtransdf)
#Price
gm<- lm(Earn~log(Price), data = gdata)
gm1<- lm(Earn~scale(poly(Price,2)), data = gdata)
gm2<- lm(log(Earn)~Price, data = gdata)
#need_fractrions
gm<- lm(Earn~log(need_fraction), data = gdata)
gm1<- lm(Earn~scale(poly(need_fraction,2)), data = gtransdf)
gm2<- lm(log(Earn)~need_fraction, data = gdata)

#all

stargazer(gm,gm1,gm2, header = FALSE, align = TRUE, title ="Table 1. Graduate Earning", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")


```
















# Handling missing data
There missing data by Public, SAT and need_fraction

```{r}
# Creating a new dataframe to transform. 
gtransdf<- gdata
gtransdf$Public_miss <-ifelse(is.na(gtransdf$Public), 1, 0)
gtransdf$SAT_miss <-ifelse(is.na(gtransdf$SAT), 1, 0) 
gtransdf$needf_miss <-ifelse(is.na(gtransdf$need_fraction), 1, 0) 
head(gtransdf)

missmodel1 <- lm(needf_miss~Earn, data = gtransdf)
missmodel1a <- lm(needf_miss~Price, data = gtransdf)
missmodel1b <- lm(needf_miss~need_fraction, data = gtransdf)
missmodel1c <- lm(needf_miss~Public, data = gtransdf)
missmodel1d <- lm(needf_miss~Price+Earn+need_fraction+Public, data = gtransdf)
missmodel1e <- lm(needf_miss~Public_miss+SAT_miss, data = gtransdf)




missmodel2 <- lm(SAT_miss~Earn+Price+SAT+Public+need_fraction, data = gtransdf)
missmodel3 <- lm(needf_miss~Earn+Price+SAT+Public+need_fraction, data = gtransdf)
mssmodel <- lm(Earn~Public_miss+SAT_miss+needf_miss, data = gtransdf)

stargazer(missmodel1, header = FALSE, align = TRUE, title ="Table 1. Graduate Earning", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")
stargazer(missmodel1,missmodel1a,missmodel1b,missmodel1c, missmodel1d,missmodel1e, header = FALSE, align = TRUE, title ="Table 1. Graduate Earning", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")


#Missing values imputing

gtransdf$SAT[is.na(gtransdf$SAT)]<-mean(gtransdf$SAT, na.rm = TRUE)
gtransdf$need_fraction[is.na(gtransdf$need_fraction)]<-mean(gtransdf$need_fraction, na.rm = TRUE)
gtransdf$Public[is.na(gtransdf$Public)]<-0
summary(gtransdf)
table(gdata$Public)

```
With NO misisng vlaue

```{r}


gmodelyesm <- lm(Earn~Public+scale(log(SAT))+scale(log(Price))+scale(log(need_fraction)), data = gdata)
gmodelnom <- lm(Earn~Public+scale(poly(SAT,2))+scale(poly(Price,2))+scale(poly(need_fraction,2)), data = gtransdf)
stargazer(gmodelnom,gmodelyesm, header = FALSE, align = TRUE, title ="Table 1. Graduate Earning", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")



stargazer(gmodel,gmodel1,gmodel2,gmodel3, header = FALSE, align = TRUE, title ="Table 1. Graduate Earning", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")


#SAT
gm<- lm(Earn~log(SAT), data = gtransdf)
gm1<- lm(Earn~scale(poly(SAT,2)), data = gtransdf)
gm2<- lm(log(Earn)~SAT, data = gtransdf)
#Price
gm<- lm(Earn~log(Price), data = gtransdf)
gm1<- lm(Earn~scale(poly(Price,2)), data = gtransdf)
gm2<- lm(log(Earn)~Price, data = gtransdf)
#need_fractrions
gm<- lm(Earn~log(need_fraction), data = gtransdf)
gm1<- lm(Earn~scale(poly(need_fraction,2)), data = gtransdf)
gm2<- lm(log(Earn)~need_fraction, data = gtransdf)

#all

stargazer(gm,gm1,gm2, header = FALSE, align = TRUE, title ="Table 1. Graduate Earning", type = "html", single.row = TRUE, out = "/home/ds/Desktop/eco.html")
```